\Title

### 2021-06-03 latex/paper/main.tex
Wrote the energy gain for O1, need to show exit from Epi and then do O2

%/========== Proof ==========/%
\section{Proof of Theorem \ref{thm:acrobot-energy-stabilization}}\label{sec:proof}
Theorem \ref{thm:acrobot-energy-stabilization} proves that the acrobot gains
energy on \(\mathcal{O}_1\) and \(\mathcal{O}_2(\bar{\rho})\), which are
sublevel sets of the nominal pendulum's energy \eqref{eqn:nominal-energy}.
%To prove Theorem \ref{thm:acrobot-energy-stabilization}, we will find conditions
%under which the acrobot gains energy on an open ``energy annulus",
%\begin{equation*}
%    \mathcal{D} := \{(q_u,p_u) \in \SxR \mid \\
%    E_0 < E(q_u,p_u) < E_1\}
%    ,
%\end{equation*}
%where \(E_1 > E_0\) are energy values, which we will choose later.

Here is the fundamental idea of this proof: for certain subsets
\(D \subset \SxR\), one can find a change of coordinates into 
pseudo-polar coordinates adapted to level sets of \(E\) 
(see Mohammadi \etal \cite{dynamic_vhcs_stabilize_closed_orbits}).
In other words, when \(I = 0\) in \eqref{eqn:acrobot-constraint}, one can find
a diffeomorphism \(T(q_u,p_u) = (r,\theta)\), where \(r\)
chooses a level set of \(E\) and \(\theta\) chooses a point on that level set.

We will explicitly calculate these transformations later;
what matters is that the dynamics of \((r,\theta)\) will satisfy 
\(\dot{r} = 0\) and \(\dot{\theta} > 0\) when \(I = 0\).
By continuity of the constrained dynamics with respect to \(I\), this implies 
there exists a small enough value \(I > 0\) so that \(\dot{\theta} > 0\) for the
acrobot.
This property will enable us to perform a time-scaling transformation 
\(t = t(\theta)\), and study how the pseudo-radius \(r\) evolves as a function
of the pseudo-angle \(\theta\), rather than as a function of time.
If \(r(\theta)\) increases on average, then \(E\) must also be increasing
on average and the constrained dynamics must be gaining energy on \(D\).
This idea is formalized in the following lemma.

\begin{lemma}\label{lemma:energy-regulation-D}
    Consider the simplified acrobot \eqref{eqn:acrobot-hamiltonian} constrained
    by the VNHC \eqref{eqn:acrobot-constraint}, whose constrained dynamics are
    parameterized by \((q_u,p_u) \in \SxR\).
    Let \(D \subset \SxR\) be open and 
    let \(]\underline{r}, \overline{r}[ \, \subset \R_{> 0}\).
    Suppose there exists a diffeomorphism 
    \begin{align*}
        T : D &\to ]\underline{r},\overline{r}[ \, \times \Sone \\
        (q_u,p_u) &\mapsto (r,\theta)
        ,
    \end{align*}
    satisfying \(\dot{r} \equiv 0\) and \(\dot{\theta} > 0\) when
    \(I = 0\).
    Let \(g(\theta,r,I) = \dot{r}/\dot{\theta}\) and assume that 
    \((\partial g/\partial r)(\theta,r,0) \equiv 0\).
    Define \(b(\theta,r_0) = (\partial g/\partial I)(\theta,r_0,0)\);
    assume it is \(2\pi\)-periodic in \(\theta\) for any fixed \(r_0\),
    and that there exists \(\epsilon > 0\) such that 
    \[
        S(r_0) := \int \limits_0^{2\pi} b(\sigma,r_0)d\sigma \geq \epsilon
        ,
    \]
    for all \(r_0 \in \, ]\underline{r},\overline{r}[\).
    Then there exists \(I^\star > 0\) small enough that the constrained dynamics
    gain energy on \(D\) for all \(I \in \,]0, I^\star]\), and lose energy on \(D\)
    for all \(I \in [-I^\star, 0[\).
\end{lemma}
\begin{proof}
    Since \(\dot{\theta} > 0\) when \(I = 0\) and the constrained dynamics 
    in \((r,\theta)\) coordinates are continuous in \(I\), there exists 
    \(I_1 > 0\) small enough that \(\dot{\theta} > 0\) for all
    \(I \in \, ]0,I_1]\).
    Hence, we can perform a time reparameterization \(t = t(\theta)\) to get a
    time-scaled pseudo-radius \(\hat{r}(\theta) := r(t(\theta))\).
    This reduces the system \((\dot{r},\dot{\theta})\) into the scalar
    time-varying ODE 
    \begin{equation}\label{eqn:rhat-ode}
        \begin{cases}
            \hat{r}^\prime= \frac{\dot{r}}{\dot{\theta}} =
            g(\theta,\hat{r},I)
            , \\
            \hat{r}(0) = r_0
            ,
        \end{cases}
    \end{equation}
    where the prime denotes differentiation by \(\theta\) and 
    \(r_0 \in \, ]\underline{r},\overline{r}[\) is the initial condition.

    Let \(\hat{r}(\theta,r_0,I)\) be the solution to \eqref{eqn:rhat-ode}.
    Taking the Taylor expansion of this solution around \(I = 0\) we get
    \(\hat{r}(\theta,r_0,I) = \hat{r}(\theta,r_0,0) + I\hat{r}_1(\theta,r_0) 
    + R(\theta,r_0,I)\). 
    Here, \(\hat{r}(\theta,r_0,0) \equiv r_0\) for all \(\theta\),
    the function \(\hat{r}_1(\theta,r_0)\) is the solution to
    \begin{equation}\label{eqn:r1-hat-prime}
        \begin{cases}
        \hat{r}_1^\prime = 
        \frac{\partial g}{\partial \hat{r}}(\theta,r_0,0)\hat{r}_1 +
        \frac{\partial g}{\partial I}(\theta,r_0,0)
        , \\
        \hat{r}_1(0) = 0
        ,
    \end{cases}
    \end{equation}
    and the remainder \(R(\theta,r_0,I)\) is \(O(I^2)\).

    Our assumption that \((\partial g/\partial r)(\theta,r_0,0) \equiv 0\)
    implies that \((\partial g/\partial \hat{r})(\theta,r_0,0) \equiv 0\).
    The solution of \ref{eqn:r1-hat-prime} can be obtained by quadrature, giving
    \[
        \hat{r}_1(\theta,r_0) = \int\limits_0^\theta b(\sigma,r_0)d\sigma
        ,
    \]
    with \(b(\theta,r_0) := (\partial g/\partial I)(\theta,r_0,0)\). 
    Since and \(\dot{\theta} > 0\) and \(b(\theta,r_0)\) is \(2\pi\)-periodic in
    \(\theta\), there is a well-defined Poincar\'{e} map describing
    how \(\hat{r}\) changes each time \(\theta\) increases by \(2\pi\).
    This map is 
    \begin{align*}
        P : \, ]\underline{r},\overline{r}[ &\to \mathbb{R}_{\geq 0} \\
        r_0 &\mapsto \hat{r}(2\pi,r_0,I)
        ,
    \end{align*}
    which expands to \(P(r_0) = r_0 + IS(r_0) + R(2\pi,r_0,I)\).
    Hence, we can understand the evolution of \(\hat{r}\) by studying
    the dynamics of the discrete-time system
    \begin{equation}\label{eqn:r-discrete}
        r_{n+1} = r_n + IS(r_n) + R(2\pi,r_n,I)
        ,
    \end{equation}
    with initial condition \(r_0\).
    Here, \(r_n\) corresponds to the distance along the line segment
    \(L := ]\underline{r},\overline{r}[ \, \times \{0\}\)
    when an orbit of \((r,\theta)\) hits \(L\) for the the \(n^\text{th}\) time,
    assuming the orbit was initialized at \((r,\theta) = (r_0,0)\).

    Proving the constrained dynamics gain energy on \(D\) is equivalent to
    proving \(\hat{r}_{n}\) eventually reaches \(\overline{r}\).
    Thanks to \cite[Theorem 10.1]{khalil_nonlinear}, 
    we know there exists some \(I_2 \in ]0,I_1]\) and \(\delta > 0\)
    such that \(\left|R(2\pi,r_n,I)\right| \leq \delta I^2\) for all 
    \(I \in [-I_2,I_2]\).
    Taking this fact alongside the assumption that \(S(r_0)\) is uniformly
    bounded below by \(\epsilon\), we can find a lower bound on
    \eqref{eqn:r-discrete}:
    \[
        r_{n+1} \geq r_n + I\epsilon - \delta I_2^2
        .
    \]
    Choosing \(I^\star \in ]0,I_2]\) small enough makes 
    \(I\epsilon - \delta I_2^2 \geq \gamma > 0\) for all \(I \in ]0,I^\star]\).
    Therefore, \(r_{n+1} \geq r_n + \gamma \geq r_0 + n\gamma\), which means all
    solutions of \eqref{eqn:r-discrete} flow towards \(\overline{r}\).
    We conclude that, for \(I \in ]0, I^\star]\), the constrained dynamics gain
    energy on \(D\).
    Changing the sign of \(I\) means \(r_{n+1} \leq r_n - n\gamma\), in which
    case the constrained dynamics lose energy on \(D\).
\end{proof}

We will now prove the first part of Theorem
\ref{thm:acrobot-energy-stabilization}.
To apply Lemma \ref{lemma:energy-regulation-D}, we choose \(D\) to be the
annulus \(\mathcal{O}_1 \backslash \{(0,0)\}\) consisting of all oscillations of
the nominal pendulum.
Using the procedure described by Mohammadi \etal 
\cite{dynamic_vhcs_stabilize_closed_orbits} for finding pseudo-polar
coordinates adapted to level sets of \(E\), we compute
\begin{align}
    \label{eqn:r-osc}
    r &= \arccos\left(\cos(q_u) - \frac{p_u^2}{30m^2gl^3}\right)
    , \\
    \label{eqn:theta-osc}
    \theta &=
    \left.\arctan_2\left(-\sign{p_u}\sqrt{1-\frac{q_u^2}{r^2}},\frac{q_u}{r}\right)
    \right|_{r = r(q_u,p_u)}
    ,
\end{align}
where \(r \in \, ]0,\pi[\).
We now verify these coordinates satisfy the requirements of 
Lemma \ref{lemma:energy-regulation-D}.
When \(I = 0\) we have \(\dot{r} = 0\) and
\begin{equation} \label{eqn:theta-dot-nom-osc}
    \dot{\theta} = \sqrt{\frac{6g}{5l}} 
        \sqrt{\frac{\cos(r\cos(\theta)) - \cos(r)}
            {r^2 \sin(\theta)^2}}
    .
\end{equation}
Note that ~\eqref{eqn:theta-dot-nom-osc} has removable singularities at
\(\theta \in \{0,\pi\}\).
Taking the limit as \(\theta\) approaches these points yields
\begin{equation*}
    \lim\limits_{\theta \to 0}\dot{\theta} 
    = \lim\limits_{\theta \to \pi} \dot{\theta}
    = \sqrt{\frac{6g \sin(r)}{10lr}}
    , 
\end{equation*}
which is smooth and well-defined for all
\(r \in \, ]0,\pi[\).
Taking these removable singularities into account,
one can verify that \(\dot{\theta} > 0\) for every \(r \in \, ]0,\pi[\).
Setting \(g(\theta,r,I) = \dot{r}/\dot{\theta}\), MATLAB symbolic computations
confirm that \((\partial g/\partial r)(\theta,r,0) \equiv 0\) as required.
Next, we compute
\begin{equation*}
    b(\theta,r_0) = 
    \frac{\partial g}{\partial I}(\theta, r_0, 0) = K a(\theta,r_0)
    ,
\end{equation*}
where
\begin{align*}
    K &:= \frac{\bar{q}_a \sqrt{30m^2g l^3}}{15}
    , \\
    a(\theta,r_0) &:= \frac{
        r_0 |\sin(\theta)| \left(
        5 c_{r_0} \cos(r_0 c_\theta) - 8 \cos(r_0c_\theta)^2 + 3
    \right)
    }{
    \sin(r_0)\sqrt{\cos(r_0c_\theta) - c_{r_0}}
    }
    .
\end{align*}
Notice that \(a(\theta,r_0)\) does not depend on the physical parameters of the
acrobot.

\textbf{TODO: write about Qro, show the figure, apply lemma to D,
    prove origin is unstable, show orbits will go through Epi, 
    then derive the constrained dynamics for the rotation domain and apply lemma
    there, concluding that O2 is O1 U Epi U rotation domain and is therefore
    also gaining energy.}

>>>>

%/========== Proof ==========/%
\section{Proof of Theorem \ref{thm:acrobot-energy-stabilization}}\label{sec:proof}
Theorem \ref{thm:acrobot-energy-stabilization} proves that the acrobot gains
energy on \(\mathcal{O}_1\) and \(\mathcal{O}_2(\bar{\rho})\), which are
sublevel sets of the nominal pendulum's energy
\(E(q_u,p_u)\) defined in \eqref{eqn:nominal-energy}.

Here is the fundamental idea of this proof: for certain subsets
\(D \subset \SxR\), one can find a change of coordinates into 
pseudo-polar coordinates adapted to level sets of \(E\) 
(see Mohammadi \etal \cite{dynamic_vhcs_stabilize_closed_orbits}).
That is, when \(I = 0\) in \eqref{eqn:acrobot-constraint}, one can find
a diffeomorphism \(T(q_u,p_u) = (r,\theta)\), where \(r\)
chooses a level set of \(E\) and \(\theta\) chooses a point on that level set.
We will explicitly calculate these transformations later.
What matters is that the dynamics of \((r,\theta)\) will satisfy 
\(\dot{r} = 0\) and \(\dot{\theta} > 0\) when \(I = 0\).
By continuity of the constrained dynamics with respect to \(I\), this implies 
there exists a small enough value \(I > 0\) so that \(\dot{\theta} > 0\) for the
acrobot.
This property will enable us to perform a time-scaling transformation 
\(t = t(\theta)\), and study how the pseudo-radius \(r\) evolves as a function
of the pseudo-angle \(\theta\), rather than as a function of time.
We will show that, for small enough \(I > 0\), \(r(\theta)\) increases on
average.
Thus, \(E\) must also be increasing on average and the constrained dynamics must
be gaining energy on \(D\).
This idea is formalized in the following lemma.

\begin{lemma}\label{lemma:energy-regulation-D}
    Consider the simplified acrobot \eqref{eqn:acrobot-hamiltonian} constrained
    by the VNHC \eqref{eqn:acrobot-constraint}, whose constrained dynamics are
    \eqref{eqn:acrobot-constrained-dynamics}.
    Let \(D \subset \SxR\) be open and 
    let \(]\underline{r}, \overline{r}[ \, \subset \R_{> 0}\).
    Suppose there exists a diffeomorphism 
    \begin{align*}
        T : D &\to ]\underline{r},\overline{r}[ \, \times \Sone \\
        (q_u,p_u) &\mapsto (r,\theta)
        ,
    \end{align*}
    satisfying \(\dot{r} \equiv 0\) and \(\dot{\theta} > 0\) when
    \(I = 0\).
    Let \(g(\theta,r,I) = \dot{r}/\dot{\theta}\) and assume that 
    \((\partial g/\partial r)(\theta,r,0) \equiv 0\).
    Define \(b(\theta,r_0) = (\partial g/\partial I)(\theta,r_0,0)\);
    assume it is \(2\pi\)-periodic in \(\theta\) for any fixed \(r_0\),
    and that there exists \(\epsilon > 0\) such that 
    \[
        S(r_0) := \int \limits_0^{2\pi} b(\sigma,r_0)d\sigma \geq \epsilon
        ,
    \]
    for all \(r_0 \in \, ]\underline{r},\overline{r}[\).
    Then there exists \(I^\star > 0\) small enough that the constrained dynamics
    gain energy on \(D\) for all \(I \in \,]0, I^\star]\), and lose energy on \(D\)
    for all \(I \in [-I^\star, 0[\).
\end{lemma}
\begin{proof}
    Since \(\dot{\theta} > 0\) when \(I = 0\) and the constrained dynamics 
    in \((r,\theta)\) coordinates are continuous in \(I\), there exists 
    \(I_1 > 0\) small enough that \(\dot{\theta} > 0\) for all
    \(I \in \, ]0,I_1]\).
    Hence, we can perform a time reparameterization \(t = t(\theta)\) to get a
    time-scaled pseudo-radius \(\hat{r}(\theta) := r(t(\theta))\).
    This reduces the system \((\dot{r},\dot{\theta})\) into the scalar
    time-varying ODE 
    \begin{equation}\label{eqn:rhat-ode}
        \begin{cases}
            \hat{r}^\prime= \frac{\dot{r}}{\dot{\theta}} =
            g(\theta,\hat{r},I)
            , \\
            \hat{r}(0) = r_0
            ,
        \end{cases}
    \end{equation}
    where \(\theta\) now represents time.
    The prime denotes differentiation by \(\theta\) and 
    \(r_0 \in \, ]\underline{r},\overline{r}[\) is the initial condition.

    Let \(\hat{r}(\theta,r_0,I)\) be the solution to \eqref{eqn:rhat-ode}.
    Taking the Taylor expansion of this solution around \(I = 0\) we get
    \(\hat{r}(\theta,r_0,I) = \hat{r}(\theta,r_0,0) + I\hat{r}_1(\theta,r_0) 
    + R(\theta,r_0,I)\). 
    Here, \(\hat{r}(\theta,r_0,0) \equiv r_0\) for all \(\theta\) because
    \(g(\theta,\hat{r},0) \equiv 0\).
    The function \(\hat{r}_1(\theta,r_0)\) is the solution to
    \begin{equation}\label{eqn:r1-hat-prime}
        \begin{cases}
        \hat{r}_1^\prime = 
        \frac{\partial g}{\partial \hat{r}}(\theta,r_0,0)\hat{r}_1 +
        \frac{\partial g}{\partial I}(\theta,r_0,0)
        , \\
        \hat{r}_1(0) = 0
        ,
    \end{cases}
    \end{equation}
    and the remainder \(R(\theta,r_0,I)\) is \(O(I^2)\).

    Our assumption that \((\partial g/\partial r)(\theta,r_0,0) \equiv 0\)
    implies that \((\partial g/\partial \hat{r})(\theta,r_0,0) \equiv 0\).
    The solution of \ref{eqn:r1-hat-prime} can therefore be obtained by
    quadrature, giving
    \[
        \hat{r}_1(\theta,r_0) = \int\limits_0^\theta b(\sigma,r_0)d\sigma
        ,
    \]
    with \(b(\theta,r_0) := (\partial g/\partial I)(\theta,r_0,0)\). 
    Since and \(\dot{\theta} > 0\) and \(b(\theta,r_0)\) is \(2\pi\)-periodic in
    \(\theta\), there is a well-defined Poincar\'{e} map describing
    how \(\hat{r}\) changes each time \(\theta\) increases by \(2\pi\).
    This map is 
    \begin{align*}
        P : \, ]\underline{r},\overline{r}[ &\to \mathbb{R}_{\geq 0} \\
        r_0 &\mapsto \hat{r}(2\pi,r_0,I)
        ,
    \end{align*}
    which expands to \(P(r_0) = r_0 + IS(r_0) + R(2\pi,r_0,I)\).
    In other words, we can understand the evolution of \(\hat{r}\) by studying
    the dynamics of the discrete-time system
    \begin{equation}\label{eqn:r-discrete}
        r_{n+1} = r_n + IS(r_n) + R(2\pi,r_n,I)
        ,
    \end{equation}
    with initial condition \(r_0\).
    Here, \(r_n\) corresponds to the distance along the line segment
    \(L := ]\underline{r},\overline{r}[ \, \times \{0\}\)
    when an orbit of \((r,\theta)\) hits \(L\) for the the \(n^\text{th}\) time,
    assuming the acrobot was initialized at \((r,\theta) = (r_0,0)\).

    If \(r_n \not\in \, ]\underline{r},\overline{r}[\), the orbit must have
    departed \(D\) and \eqref{eqn:r-discrete} is no longer valid.
    Proving the constrained dynamics gain energy on \(D\) is therefore
    equivalent to finding \(N \in \mathbb{Z}_{> 0}\) where 
    \(\hat{r}_{n} > \overline{r}\) for all \(n \geq N\).
    Using a perturbation analysis (see Khalil 
    \cite[Theorem 10.1]{khalil_nonlinear}),
    we know there exists some \(I_2 \in ]0,I_1]\) and \(\delta > 0\)
    such that \(\left|R(2\pi,r_n,I)\right| \leq \delta I^2\) for all 
    \(I \in [-I_2,I_2]\).
    Taking this fact alongside the assumption that \(S(r_0) \geq \epsilon\),
    we find a lower bound on \(r_{n+1}\):
    \eqref{eqn:r-discrete}:
    \[
        r_{n+1} \geq r_n + I\epsilon - \delta I_2^2
        .
    \]
    Choosing \(I^\star \in ]0,I_2]\) small enough makes 
    \(I\epsilon - \delta I_2^2 \geq \gamma > 0\) for all \(I \in ]0,I^\star]\).
    Therefore, \(r_{n} \geq r_{n-1} + \gamma \geq r_0 + n\gamma\), 
    so all solutions of \eqref{eqn:r-discrete} eventually flow past
    \(\overline{r}\).
    We conclude that, for \(I \in ]0, I^\star]\), the constrained dynamics gain
    energy on \(D\).

    Changing the sign of \(I\) changes the direction of all the
    above inequalites, which implies \(r_{n} \leq r_0 - n\gamma\). 
    In this case all orbits of \eqref{eqn:r-discrete} flow below
    \(\underline{r}\), i.e., the constrained dynamics lose energy on \(D\).
\end{proof}

\subsection{Energy gain on \(\mathcal{O}_1\)}
We will now prove the first part of Theorem
\ref{thm:acrobot-energy-stabilization}.
We choose \(D\) in Lemma \ref{lemma:energy-regulation-D} to be the
annulus \(\mathcal{O}_1 \backslash \{(0,0)\}\) consisting of all oscillations of
the nominal pendulum.
Using the procedure described by Mohammadi \etal 
\cite{dynamic_vhcs_stabilize_closed_orbits} for finding pseudo-polar
coordinates adapted to level sets of \(E\), we compute
\begin{align}
    \label{eqn:r-osc}
    r &= \arccos\left(\cos(q_u) - \frac{p_u^2}{30m^2gl^3}\right)
    , \\
    \label{eqn:theta-osc}
    \theta &=
    \left.\arctan_2\left(-\sign{p_u}\sqrt{1-\frac{q_u^2}{r^2}},\frac{q_u}{r}\right)
    \right|_{r = r(q_u,p_u)}
    ,
\end{align}
where \(r \in \, ]0,\pi[\).
We now verify these coordinates satisfy the requirements of 
Lemma \ref{lemma:energy-regulation-D}.

When \(I = 0\) we have \(\dot{r} = 0\) and
\begin{equation} \label{eqn:theta-dot-nom-osc}
    \dot{\theta} = \sqrt{\frac{6g}{5l}} 
        \sqrt{\frac{\cos(r\cos(\theta)) - \cos(r)}
            {r^2 \sin(\theta)^2}}
    .
\end{equation}
Note that ~\eqref{eqn:theta-dot-nom-osc} has removable singularities at
\(\theta \in \{0,\pi\}\).
Taking the limit as \(\theta\) approaches these points yields
\begin{equation}\label{eqn:theta-dot-limit}
    \lim\limits_{\theta \to 0}\dot{\theta} 
    = \lim\limits_{\theta \to \pi} \dot{\theta}
    = \sqrt{\frac{6g \sin(r)}{10lr}}
    , 
\end{equation}
which is smooth and well-defined for all
\(r \in \, ]0,\pi[\).
From \eqref{eqn:theta-dot-nom-osc}-\eqref{eqn:theta-dot-limit},
one can verify that \(\dot{\theta} > 0\) for every \(r \in \, ]0,\pi[\).
Defining \(g(\theta,r,I) = \dot{r}/\dot{\theta}\), MATLAB symbolic computations
confirm that \((\partial g/\partial r)(\theta,r,0) \equiv 0\) as required.

Next we compute
\(b(\theta,r_0) = (\partial g/\partial I)(\theta, r_0, 0) = K a(\theta,r_0)\),
where
\begin{align*}
    K &:= \frac{\bar{q}_a \sqrt{30m^2g l^3}}{15}
    , \\
    a(\theta,r_0) &:= \frac{
        r_0 |\sin(\theta)| \left(
        5 c_{r_0} \cos(r_0 c_\theta) - 8 \cos(r_0c_\theta)^2 + 3
    \right)
    }{
    \sin(r_0)\sqrt{\cos(r_0c_\theta) - c_{r_0}}
    }
    .
\end{align*}
Notice that \(K\) is a positive constant which depends only on
\(m\),\(g\),\(l\), and \(\bar{q}_a\).
This means that there exists \(\epsilon > 0\) such that 
\(S(r_0) := \int_0^{2\pi} b(\sigma,r_0)d\sigma \geq \epsilon\)
if and only if \(Q(r_0) := \int_0^{2\pi} a(\sigma,r_0) d\sigma\) is strictly
positive for all \(r_0 \in \, ]0,\pi[\).
Since \(a(\theta,r_0)\) is adimensional, we can numerically compute \(Q(r_0)\)
once for all acrobots.
The plot of \(Q(r_0)\) when \(r_0 \in [10^{-10}, \pi - 10^{-3}]\) is shown in
Figure \ref{fig:acrobot-Q}.
We see that it is strictly positive and monotonically increasing, with an
asymptote at \(r_0 = \pi\).
Simulations with smaller \(r_0\) result in an infinite integral error due to a
division by zero, yet we believe the \(Q(r_0)\) is in fact positive for all 
\(r_0 \in \, ]0,\pi[\).

\begin{figure}
    \centering
    % TODO: Show this plot
    %\includegraphics[width=0.8\linewidth]{}
    \caption{The plot of \(Q(r_0)\).}
    \label{fig:acrobot-Q}
\end{figure}

Finally, \(a(\theta,r_0)\) is clearly \(2\pi\)-periodic in \(\theta\),
which means all conditions of Lemma \ref{lemma:energy-regulation-D}
are satisfied. 
Therefore, the acrobot is gaining energy everywhere on
\(D = \mathcal{O}_1 \backslash \{(0,0)\}\).
The origin must be a repeller (otherwise Lemma
\ref{lemma:energy-regulation-D} would fail), so we conclude that the acrobot
is gaining energy on \(\mathcal{O}_1\).

\textbf{TODO: show orbits will go through Epi, 
    then derive the constrained dynamics for the rotation domain and apply lemma
    there, concluding that O2 is O1 U Epi U rotation domain and is therefore
    also gaining energy.}
